\textbf{Computational Fuzzy Extractors}

### 2013-05-17 CompFuzzExt.tex
working on intro and section 4

By considering this computational secrecy requirement, we construct the first \emph{lossless} (computational) fuzzy extractors, where the derived key $r$ is as long as the entropy of the source $w$. % without conditioning on anything---i.e., before $\gen$ is run (see~\thref{thm:lossless secure conductor log})).  
Our construction of lossless fuzzy extractors~(\consref{cons:informal construction}) is based on the Learning with Errors~(LWE) assumption due to Regev~\cite{regev2005LWE, regevLWEsurvey},  which says that decoding a random linear code is computationally difficult.  
%We show that this relaxation of the security requirement is  useful.  Specifically, we also define the notion of computational fuzzy extractors, in which the extracted key is required to be pseudorandom---i.e., to look random to any computationally bounded observer.
%We show that our relaxed notion of secure sketches is sufficient to construct computational  fuzzy extractors via a simple and efficient construction, utilizing reconstructive extractors~\cite{barak-computational}.  The resulting fuzzy extractor produces a key that is as long as the entropy of $w$, minus only the loss necessary in any extractor construction.
%\lnote{it would be good to find another application} 
Our lossless fuzzy extractor is built via the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} used in prior work.  To apply the LWE assumption, we correct errors of a random linear code, which limits our decoding algorithm to reconciling a logarithmic number of differences.

The recent result of D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} shows the hardness of LWE when the error vector comes from the uniform distribution, with each coordinate ranging over a small interval.  This allows us to directly use our source $w$ as the LWE error vector.  To utilize the result of~\cite{dottling2012}, we need to assume that the input comes from the uniform distribution. We are able to relax this limitation and allow $w$ to come from a symbol-fixing source~\cite{KZ07} (each dimension is either uniform or fixed). This relaxation requires new results about the hardness of LWE when samples have a fixed~(and adversarially known) error vector, which may be of independent interest~(\thref{thm:blockLWE}).

>>>>

By considering this computational secrecy requirement, we construct the first \emph{lossless} computational fuzzy extractors (\consref{cons:informal construction}), where the derived key $r$ is as long as the entropy of the source $w$. It is uses the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} used in prior work, but with two crucial differences.  First, the key $r$ is not extracted from $w$ like in the sketch-and-extract approach; rather $w$ ``encrypts'' $r$ in a way that is decryptable with the knowledge of some close $w'$. Second, the code used is a random linear code, which allows us to use the Learning with Errors~(LWE) assumption due to Regev~\cite{regev2005LWE, regevLWEsurvey} to get a long $r$ out.

Specifically,  we use the  recent result of D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012}, which shows the hardness of decoding random linear codes when the error vector comes from the uniform distribution, with each coordinate ranging over a small interval. This allows us to use $w$ as the error vector, assuming it is uniform.  We also use a result of Akavia, Goldwasser, and Vaikuntanathan~\cite{akavia2009},  which says that LWE has many hardcore bits, to hide $r$.

Because we use a random linear code,  our decoding is limited to reconciling a logarithmic number of differences.  Unfortunately, we  cannot utilize the results that improve the decoding radius through the use of trapdoors (such as \cite{regev2005LWE}), because in a fuzzy extractor, there is no secret storage place for the trapdoor.

%We show that this relaxation of the security requirement is  useful.  Specifically, we also define the notion of computational fuzzy extractors, in which the extracted key is required to be pseudorandom---i.e., to look random to any computationally bounded observer.
%We show that our relaxed notion of secure sketches is sufficient to construct computational  fuzzy extractors via a simple and efficient construction, utilizing reconstructive extractors~\cite{barak-computational}.  The resulting fuzzy extractor produces a key that is as long as the entropy of $w$, minus only the loss necessary in any extractor construction.
%\lnote{it would be good to find another application}

We are able to relax the assumption that $w$ comes from the uniform distribution, and instead allow $w$ to come from a symbol-fixing source~\cite{KZ07} (each dimension is either uniform or fixed). This relaxation follows from new results about the hardness of LWE when samples have a fixed~(and adversarially known) error vector, which may be of independent interest~(\thref{thm:blockLWE}). See Section~\ref{}.
